\vspace{-10ex}%
\rule{\textwidth}{0.3pt}
\vspace{5ex}
 % after-code


I would like to thank the personal at Followit to taking me in and helping me through the project time. A special thanks to Bengt Evertsson for his supervision and help. 

A big thanks goes to my supervisor Jonny Johansson at LTU for his support and guidance in the project.
And a big thanks goes to my lovley fiancee Sara Andersson for her support and strong patience throughout the whole project. 

\begin{flushright}
Josef Lundberg
\newline
Lindesberg, \today
\end{flushright}

\begin{comment}
- Rätta till bilden med VHF skalan
- Räkna och visa den koplexa polerna mm för chebychev


\newglossaryentry{apig}{name={API},
    description={An Application Programming Interface (API) is a particular set
    of rules and specifications that a software program can follow to access and
    make use of the services and resources provided by another particular software
    program that implements that API. }}
%%% SWD
\newglossaryentry{swdg}{name={SWD},
    description={Serial Wire Debug (SWD) is an alternative 2-pin electrical interface,
	standard debugging protocol used in ARM processors.}}

\newglossaryentry{swd}{type=\acronymtype, name={SWD},
description={Serial Wire Debug}, 
first={Serial Wire Debug (SWD)\glsadd{swdg}}}
%%% define the acronym and use the see= option
\newglossaryentry{api}{type=\acronymtype, name={API}, 
description={Application Programming Interface}, 
first={Application Programming Interface (API)\glsadd{apig}}, see=[Glossary:]{apig}}
%%% TOF
\newglossaryentry{tofg}{name={ToF},
    description={Time of Flight (TOF) is a property of an object, particle, electromagnetic or other wave. It is the time that such an object needs to travel a distance through a medium. The measurement of this time (i.e. the time of flight) can be used for a time standard as a way to measure velocity or path length through a given medium.}}
\newglossaryentry{tof}{type=\acronymtype, name={ToF}, 
description={Time of Flight}, 
first={Time of Flight (TOF)\glsadd{tofg}}, see=[Glossary:]{tofg}}
%%% NMEA
\newglossaryentry{nmeag}{name={NMEA},
    description={The National Marine Electronics Association (NMEA) standard is a
    specification that defines the interface between various pieces of marine electronic equipment.}}
\newglossaryentry{nmea}{type=\acronymtype, name={NMEA}, 
description={National Marine Electronics Association standard}, 
first={National Marine Electronics Association standard (NMEA)\glsadd{nmeag}}}


%%% PNG
\newglossaryentry{pngg}{name={PNG},
description={ddddddddddddddddddddddddddddd}}

\newglossaryentry{png}{type=\acronymtype, name={PNG}, 
description={Portable Network Graphics (PNG) is a raster graphics file format.}, 
first={Portable Network Graphics (PNG)\glsadd{pngg}}}
\end{comment}

%\thispagestyle{empty}