\begin{thebibliography}{99}
\label{sec:ref}
\addcontentsline{toc}{section}{\nameref{sec:ref}}

%%% BLANK LINKS
\bibitem{cad}
	\url{https://www.autodesk.com/products/fusion-360/overview}
\bibitem{wind_meas}
	\url{ltu.diva-portal.org/smash/get/diva2:1039147/FULLTEXT01.pdf}
\bibitem{load_cell}
	\url{http://www.te.com/commerce/DocumentDelivery/DDEController?Action=srchrtrv&DocNm=FX19&DocType=DS&DocLang=English}
\bibitem{webpage}
	\url{http://www.lygte-info.dk/info/battery\%20protection\%20UK.html}
%%% LINKS WITH DESCRIPTIONS
\bibitem{lm1117}
	KiCad library entry for voltage regulator component lm1117 by \emph{ObKo}, 2012,
	\url{https://github.com/ObKo/kicad-libraries/blob/master/libraries/lm1117.lib}.
\bibitem{overprotection}
	Overvoltage and Reverce-voltage Protection in Automotive Systems,
	Application note 760, \emph{Maxim integrated}, Apr 02, 2002, 
	\url{https://www.maximintegrated.com/en/app-notes/index.mvp/id/760}.
\bibitem{Tof_cover}
	\gls{st}, Application note: AN4907, \emph{VL53L0X ranging module cover window guidelines},
	\url{http://www.st.com/content/ccc/resource/technical/document/application_note/group0/9d/93/be/33/13/be/46/19/DM00326504/files/DM00326504.pdf/jcr:content/translations/en.DM00326504.pdf}
\bibitem{kf eff}
	Duygun, M., Kutlu, L. \& Sickles, R.C., Journal of Productivity Analysis, 2016, 46: 155, \url{https://doi.org/10.1007/s11123-016-0477-z}
%%% NO LINK STUFF
\bibitem{cccv}
	Power Guy, \emph{Constant Current Constant voltage}, May 26, 2016, San Diego, USA,
	\url{https://www.us.tdk-lambda.com/media/292143/tdk-lambda-blog-052616.pdf}.
\bibitem{animal} 
	D.L. Hall and J. Llinas, \emph{An introduction to multisensor data fusion}, 
	Proceedings of the IEEE, 85(1):6 –23, jan 1997.
\bibitem{boken} 
	B.R. Grover H, Patrick, \emph{Introduction to random signals and applied Kalman filtering}, 1997. 
\bibitem{SNAME} 
	Society of Naval Architects and Marine Engineers (SNAME), \emph{Principles of Naval Architecture}, 1989, Vol. III, \emph{SNAME}. 
\bibitem{nonlinear} 
	Dr. Oliver Nelles, \texttt{nonlinear system identification}.
\bibitem{non-linear}
	Noureldin., Karamat T.B., Georgy J., 2013, \texttt{ Basic Navigational Mathematics, Reference Frames and the Earth’s Geometry. In: Fundamentals of Inertial Navigation, Satellite-based 	Positioning and their Integration}, Springer, Berlin, Heidelberg.
\bibitem{animal}
	D.L. Hall and J. Llinas. \emph{An introduction to multisensor data fusion}, Proceedings of the. IEEE, 85(1):6 –23, jan 1997.
\bibitem{signal_process}
	Henry Stark, John W Woods, \emph{Probability and Random Processes with Applications to Signal Processing}, 4/E 2012,
	 Pearson Higher Education.
\bibitem{Discrete_kalman}
	Donald E. Catlin, \emph{Estimation, Control, and the Discrete Kalman Filter}, 1989.
\bibitem{book}
	Weicker, P., \emph{A Systems Approach to Lithium-ion Battery Management}, Boston, Artech House, 2014.
\end{thebibliography}
