%%% API
%%% The glossary entry the acronym links to   

%%% ADC
\newglossaryentry{adcg}{name={ADC},
    description={An Analog-to-digital converter (ADC) is a system that converts 
    an analog signal into a digital signal.}}

\newglossaryentry{adc}{type=\acronymtype, name={ADC}, 
description={Analog-to-digital converter}, 
first={Analog-to-digital converter (ADC)\glsadd{adcg}}}


%%% CAD
\newglossaryentry{cadg}{name={CAD},
    description={Computer-aided design (CAD) is a computer system which aids
    the creation and modification of some kind of design.}}

\newglossaryentry{cad}{type=\acronymtype, name={CAD}, 
description={Computer-aided design (CAD) is a computer system which aids
    the creation and modification of some kind of design.}, 
first={Computer-aided design (CAD)\glsadd{cadg}}}


%%% DRC
\newglossaryentry{drcg}{name={DRC},
    description={Design Rule Check (DRC) is an automated check of your designed \gls{pcb}
	to see if it follows all specified design rules.}}

\newglossaryentry{drc}{type=\acronymtype, name={DRC}, 
description={Design Rule Check}, 
first={Design Rule Check (DRC)\glsadd{drcg}}}


%%% ERC
\newglossaryentry{ercg}{name={ERC},
    description={Electronic Rule Check (ERC) is an automated check of your designed schematic
	to see if it follows all electronic rules.}}

\newglossaryentry{erc}{type=\acronymtype, name={ERC}, 
description={Electronic Rule Check}, 
first={Electronic Rule Check (ERC)\glsadd{ercg}}}


%%% GPIO
\newglossaryentry{gpiog}{name={GPIO},
    description={General Purpose Input Output (GPIO), is a general use port of an \gls{mcu}.}}

\newglossaryentry{gpio}{type=\acronymtype, name={GPIO}, 
description={General Purpose Input Output}, 
first={General Purpose Input Output (GPIO)\glsadd{gpiog}},}


%%% GPS
\newglossaryentry{gpsg}{name={GPS},
    description={The Global Positioning System (GPS) is a radionavigation
    system owned by the United States government and operated by the 
    United States Air Force. It uses sattelites for geolocation and time.}}

\newglossaryentry{gps}{type=\acronymtype, name={GPS}, 
description={The Global Positioning System (GPS) is a radionavigation
    system owned by the United States government and operated by the 
    United States Air Force. It uses sattelites for geolocation and time.}, 
first={Global Positioning System (GPS)\glsadd{gpsg}}}


%%% I2C
\newglossaryentry{i2cg}{name={I$^2$C},
    description={Inter-Integrated Circuit (I$^2$C), is a serial computer bus.}}

\newglossaryentry{i2c}{type=\acronymtype, name={I$^2$C}, 
description={Inter-Integrated Circuit}, 
first={Inter-Integrated Circuit (I$^2$C)\glsadd{i2cg}}}


%%% IC
\newglossaryentry{icg}{name={IC},
    description={Integrated Circuit (IC) is a set of electronic circuits on one small flat chip.}}

\newglossaryentry{ic}{type=\acronymtype, name={IC}, 
description={Integrated Circuit (IC) is a set of electronic circuits on one small flat chip.}, 
first={Integrated Circuit (IC)\glsadd{icg}}}


%%% IMU
\newglossaryentry{imug}{name={IMU},
    description={Inertial Measurement Units (IMUs) are integrated circuits that
    can measure acceleration, rotational velocity and magnetic field strength.}}

\newglossaryentry{imu}{type=\acronymtype, name={IMU}, 
description={Inertial Measurement Units (IMUs) are integrated circuits that
    can measure acceleration, rotational velocity and magnetic field strength.}, 
first={Inertial Measurement Unit (IMU)\glsadd{imug}}}


%%% IPC
\newglossaryentry{ipcg}{name={IPC},
    description={Institute for Printed Circuits (IPC), Institute for Interconnecting and Packaging Electronic Circuits}}

\newglossaryentry{ipc}{type=\acronymtype, name={IPC}, 
description={Institute for Printed Circuits}, 
first={Institute for Printed Circuits (IPC)\glsadd{ipcg}}}


%%% JTAG
\newglossaryentry{jtagg}{name={JTAG},
    description={JTAG is an industry standard for verifying designs and testing printed circuit boards after manufacture.}}

\newglossaryentry{jtag}{type=\acronymtype, name={JTAG}, 
description={JTAG is an industry standard for verifying designs and testing printed circuit boards after manufacture.}, 
first={Joint Test Action Group (JTAG)\glsadd{jtagg}}}


%%% LGA
\newglossaryentry{lgag}{name={LGA},
    description={Land Grid Array (LGA) is a type of \gls{smd} device with pins on the socket.}}

\newglossaryentry{lga}{type=\acronymtype, name={LGA}, 
description={Land Grid Array}, 
first={Land Grid Array (LGA)\glsadd{lgag}}}


%%% LDO
\newglossaryentry{ldog}{name={LDO},
    description={A low-dropout regulator is a DC linear voltage regulator that can regulate the output voltage even when the supply voltage is very close to the output voltage.}}

\newglossaryentry{ldo}{type=\acronymtype, name={LDO}, 
description={A low-dropout regulator is a DC linear voltage regulator that can regulate the output voltage even when the supply voltage is very close to the output voltage.}, 
first={Low-dropout regulator (LDO)\glsadd{ldog}}}

%%% MCU
\newglossaryentry{mcug}{name={MCU},
description={dddddddddddddddddddddddddddddddddddddddddddddddddd.}}

\newglossaryentry{mcu}{type=\acronymtype, name={MCU}, 
description={A Microcontroller Unit (MCU) is a single computer chip 
    designed for embedded applications.}, 
first={Microcontroller Unit (MCU)\glsadd{mcug}}}

%%% PC
\newglossaryentry{pcg}{name={PC},
description={dddddddddddddddddddddd.}}

\newglossaryentry{pc}{type=\acronymtype, name={PC}, 
description={Personal Computer (PC)  is a multi-purpose computer whose size,
	capabilities, and price make it feasible for individual use.}, 
first={Personal Computer (PC)\glsadd{pcg}}}


%%% PCB
\newglossaryentry{pcbg}{name={PCB},
description={dddddddddddddddddddddddddddddd.}}

\newglossaryentry{pcb}{type=\acronymtype, name={PCB}, 
description={A Printed Circuit Board (PCB) is the common acronym when
	referring to populated circuit boards.}, 
first={Printed Circuit Board (PCB)\glsadd{pcbg}}}


%%% RTC
\newglossaryentry{rtcg}{name={RTC},
description={ddddddddddddddddddddddddddddddd.}}

\newglossaryentry{rtc}{type=\acronymtype, name={RTC}, 
description={A Real time clock is an IC that is used to mesure time even when the main device is off.}, 
first={Real time clock (RTC)\glsadd{rtcg}}}

%%% SPI
\newglossaryentry{spig}{name={SPI},
description={werwrwerw.}}

\newglossaryentry{spi}{type=\acronymtype, name={SPI}, 
description={Serial Peripheral Interface Bus (SPI), is a synchronous 
    serial communication interface specification used for short distance 
    communication, primarily in embedded systems.}, 
first={Serial Peripheral Interface (SPI)\glsadd{spig}}}


%%% UART
\newglossaryentry{uartg}{name={UART},
description={ssssssssssssssssssss.}}

\newglossaryentry{uart}{type=\acronymtype, name={UART}, 
description={Universal asynchronous receiver-transmitter}, 
first={Universal asynchronous receiver-transmitter (UART)\glsadd{uartg}}}


%%% VHF
\newglossaryentry{vhfg}{name={VHF},
description={ddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddd.}}

\newglossaryentry{vhf}{type=\acronymtype, name={VHF}, 
description={Very High Frequency (VHF) is a band of frequencies in the electromagnetical spectrum}, 
first={Very High Frequency (VHF)\glsadd{vhfg}}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\thispagestyle{empty}
